Likelihood ratio tests constructed with discriminative classifiers and calibrated with generative models

### 2014-11-20 tex/parametrized-learning.tex
line numbers

\usepackage{jmlr2e}

%\jmlrheading{1}{2014}{X-XX}{4/00}{10/00}{Kyle Cranmer}

@@

Since the prior $p(y)$ has no clear meaning for the test at hand and because the classifier score $p(x|y)$ may not be well calibrated, we choose to denote the classifier score $s(x)$ and simply think of it as a deterministic dimensionality reduction map $s: X \to \mathbb{R}$.

>>>>

\usepackage{jmlr2e}
\usepackage{lineno}
\linenumbers
%\jmlrheading{1}{2014}{X-XX}{4/00}{10/00}{Kyle Cranmer}

@@

Since the prior $p(y)$ has no clear meaning for the test at hand and because the classifier score $p(y|x)$ may not be well calibrated, we choose to denote the classifier score $s(x)$ and simply think of it as a deterministic dimensionality reduction map $s: X \to \mathbb{R}$.
